### 2017-10-10 Gruba/00-abstr.tex
v4.1
v4.1

\begin{abstract}
Social media applications are emerging, with rapidly growing users and large numbers of \retd{} blogs every minute.
The variety among users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Meanwhile, building one model per user is not practical.
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} by datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
\end{abstract}
% behavior and activity in this paper are interchangeable

>>>>

\begin{abstract}
Social media applications are emerging, with rapidly growing users and large numbers of \retd{} blogs every minute.
The variety among users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model.% \cite{IEEEexample:journals/tkdd/ZhangTLLX15,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
Meanwhile, building one model per user is not practical.
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} by datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.
\end{abstract}
% behavior and activity in this paper are interchangeable

### 2017-10-10 Gruba/01-intro.tex
v4.1
v4.1

Social media is overwhelming nowadays, with massive users on Facebook \refe{}, Twitter \refe{} and Weibo \refe{} while the number of users keeps increasing.
These users behave variously, knowledge of which is significant in recommendation system, activity prediction and Big Thing analysis.
Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has attracted the attention from both academia and industry.

Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
Already, there exist work of building a single model for all the users \refe{}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well.
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.

\stitle{Contributions.}  The contributions of this work include:

>>>>

Social media is overwhelming nowadays, with massive users on Facebook, Twitter and Weibo while the number of users keeps increasing.
These users behave variously, knowledge of which is significant in recommendation system, activity prediction and Big Thing analysis.
Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry.

Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model; for example, the mono model for all users, one model per user, etc), as well as the variety of features to be selected for differentiating these units.
Already, there exist work of building a single model for all the users \refe{}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics. 
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well.
The main challenge is to properly model user groups upon behavior analysis.

\stitle{Contributions.}  
This work contributes as follows:

### 2017-10-10 Gruba/02-overview.tex
v4.1
v4.1

The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.

Informally, providing a set of users $\{U\}$ and the associated blogs $\{B\}$, as well as a blog query $b$ and a follower of $O(b)$ written as $f$, i.e., $f \in R_s(O(b))$, \sys{} shall build a \retg{} model for $(\{U\},\ \{B\})$, upon which Y/N is returned regarding whether $f$ shall \ret{} $b$.

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}, comprising three subsystems: Data Storage, Processing Runtime and Profile Demonstrator.

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{figures/architecture}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

@@

\textbf{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

\textbf{Processing Runtime.}
In the heart of \sys{} lies the Processing Runtime subsystem, which consists of three major components as follows.
\begin{enumerate}
	\item Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extractor and serve as the input of User Clusterer.
	\item User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group. 
	\item Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples to train a model, over which the testing of users' \retg{} behavior is performed.
\end{enumerate}

\textbf{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization. 
For the time being, Profile Demonstrator presents \tbc{}.

>>>>

The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
%
Informally, providing a set of users $\{U\}$ and the associated blogs $\{B\}$, as well as a blog query $b$ and a follower of $O(b)$ written as $f$, i.e., $f \in R_s(O(b))$, \sys{} shall build a \retg{} model for $(\{U\},\ \{B\})$, upon which Y/N is returned regarding whether $f$ shall \ret{} $b$.

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}, mainly comprising three subsystems: Data Storage, the central Processing Runtime and Profile Demonstrator.

\begin{figure}[!htb]
\centering
\includegraphics[width=.75\linewidth]{figures/architecture}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

@@

\stitle{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

\stitle{Processing Runtime.}
In the heart of \sys{} lies the Processing Runtime subsystem, which consists of three major components as follows.
%\begin{enumerate}

	\stab(1)  Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extractor and serve as the input of User Clusterer.

	\stab(2)  User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group.

	\stab(3)  Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples (i.e., blogs that were or weren't \retd{}) to train a model, over which the testing of users' \retg{} behavior is performed.
%\end{enumerate}

\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization.
For the time being, Profile Demonstrator presents \tbc{}.

### 2017-10-10 Gruba/03-fe.tex
v4.1
v4.1

\textit{Step 1:} Each blog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.

\textit{Step 2:} Explicit interests are explored. Specifically, every word $w$ is sent to match each cell word $c$ of lexicon topics.
If $w$ and $c$ are identical, $sim(w, c) = 1$.
Otherwise, $sim(w, c) = 0$.
As to the similarity of $b$ against a lexicon topic $t$, it is:
\begin{equation}
\label{eq:bt}
sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j)
\end{equation}
where $sim(w_i, c_j)$ refers to the similarity of a word pair.

@@

If none of $sim(b, t)$ could meet the threshold, i.e., explicit interest discovery over user $u$ fails, go to \textit{Step 3} and \textit{Step 4} in parallel, so as to ``mine'' the implicit interests of $u$.

\textit{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
\begin{equation}
\label{eq:tf}
W_f = \{(w_i, p_i)\}
\end{equation}
where $w_i$ refers to a single word, of which the weight is $p_i$, with $\sum_{\substack{i}} p_i = 1$.

@@

Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight} (see Definition \ref{eq:tf}).
Go to \textit{Step 5}.

\textit{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA \ref{IEEEexample:zhao2011comparing} to result the word weight distribution of blog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textit{Step 6}.

\textit{Step 5:} TF-IDF based similarity is calculated.
For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and:
\begin{equation}
\label{eq:sim-tf2}
sim(w_i, t) = \sum_{\substack{j}} sim(w_i, c_j)
\end{equation}
Go to \textit{Step 7}.

\textit{Step 6:} Accordingly, Twitter-LDA based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and:
\begin{equation}
\label{eq:sim-tw2}
sim(w'_i, t) = \sum_{\substack{j}} sim(w'_i, c_j)
\end{equation}
Go to \textit{Step 7}.

\textit{Step 7:} Hence, the similarity of a blog $b$ against a lexicon topic $t$ is given by:
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t)
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.
Go to \textit{Step 8}.

\textit{Step 8:} Repeat the above steps (Step 1 to Step 7) for the blog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
Such computation further extends to all the blogs owned by user $u$, such that:
$\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{t\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0,\ s_1,\ ...,\ s_{n-1})
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic $t_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, t_k)
\end{equation}

>>>>

\stitle{Step 1:} Each blog of $u$ is decomposed into a word set, i.e., $b = \{w\}$ where $b \in B_s(u)$.

\stitle{Step 2:} Explicit interests are explored. Specifically, every word $w$ is sent to match each cell word $c$ of lexicon topics.
If $w$ and $c$ are identical, $sim(w, c) = 1$.
Otherwise, $sim(w, c) = 0$.
As to the similarity of $b$ against a lexicon topic $t$, it is:
\begin{equation}
\label{eq:bt}
sim(b, t) = \sum_{\substack{i, j}} sim(w_i, c_j)
\end{equation}
where $sim(w_i, c_j)$ refers to the similarity of a word pair.

@@

If none of $sim(b, t)$ could meet the threshold, i.e., explicit interest discovery over user $u$ fails, go to \textbf{Step 3} and \textbf{Step 4} in parallel, so as to ``mine'' the implicit interests of $u$.

\stitle{Step 3:} A metric \textit{TF-IDF weight} $W_f$ is computed, i.e., employing TF-IDF (term-frequency and inverse document-frequency) to calculate the weight distribution of words in blog $b$:
\begin{equation}
\label{eq:tf}
W_f = \{(w_i, p_i)\}
\end{equation}
where $w_i$ refers to a single word, of which the weight is $p_i$, with $\sum_{\substack{i}} p_i = 1$.

@@

Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight} (see Definition \ref{eq:tf}).
Go to \textbf{Step 5}.

\stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing} 
\refe{}
to result the word weight distribution of blog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textbf{Step 6}.

\stitle{Step 5:} TF-IDF based similarity is calculated.
For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \refe{}.
Go to \textbf{Step 7}.

\begin{comment}
:
\begin{equation}
\label{eq:sim-tf2}
sim(w_i, t) = \sum_{\substack{j}} sim(w_i, c_j)
\end{equation}
\end{comment}

\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector \refe{}.
Go to \textbf{Step 7}.

\begin{comment}
:
\begin{equation}
\label{eq:sim-tw2}
sim(w'_i, t) = \sum_{\substack{j}} sim(w'_i, c_j)
\end{equation}
\end{comment}

\stitle{Step 7:} Hence, the similarity of a blog $b$ against a lexicon topic $t$ is given by:
\begin{equation}
\label{eq:simbt}
sim(b, t) = \alpha * sim(W_f, t) + (1 - \alpha) * sim(W_t, t)
\end{equation}
where the $\alpha$ is a parameter by which \sys{} could set flexible priorities between TF-IDF and Twitter-LDA.
Go to \textbf{Step 8}.

\stitle{Step 8:} Repeat the above steps (Step 1 to Step 7) for the blog $b$ over every topic in lexicon, i.e., $\forall t_k \in L$ results one similarity value of $sim(b, t_k)$.
Such computation further extends to all the blogs owned by user $u$, such that:
$\forall b_m \in B_s(u)$, $\forall t_k \in L$, there exists a similarity of $sim(b_m, t_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{t\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0,\ s_1,\ ...,\ s_{n-1})
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic $t_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, t_k)
\end{equation}

### 2017-10-10 Gruba/04-uc.tex
v4.1
v4.1

Providing the \textit{Feature Data}, User Clusterer takes the charge of grouping each user concerned into a proper cluster.
Algorithm \ref{alg:uc} illustrates such overall procedure.

The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

@@

Next, we shall now first detail how \sys{} performs the clustering task and subsequently illustrate the computation regarding the metric of Silhouette coefficient value.

@@

\begin{table}[!htb]
\centering
\begin{small}
\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_s$, $\#E_s$, $R_{ee}$, $\#B_s$, $R_{oc}$, $\#W_r$				\\	\midrule
categorical data			& $U_t$				\\	\midrule
normalized vectors			& $P_t$, $P_g$, $P_f$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

In \sys{}, Silhouette coefficient value serves as the fundamental criteria for the optimal clustering selection.
Providing a clustering result, each user is associated with a cluster.
For a given user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu-flat}.

>>>>

Providing the \textit{Feature Data}, User Clusterer takes the charge of grouping each user concerned into a proper cluster.
Algorithm \ref{alg:uc} illustrates such overall procedure.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

@@

Next, we shall now first detail how \sys{} performs the clustering task and subsequently illustrate the computation for the metric of Silhouette coefficient value.

@@

\begin{table}[!htb]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_s$, $\#E_s$, $R_{ee}$, $\#B_s$, $R_{oc}$, $\#W_r$				\\	\midrule
categorical data			& $U_t$				\\	\midrule
normalized vectors			& $P_t$, $P_g$, $P_f$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

In \sys{}, Silhouette coefficient value serves as the fundamental criteria for the optimal clustering selection.
Providing a clustering result, each user is associated with a cluster.

For a given user $u$ of cluster $l$, we employ the vector $Y$ to denote the \textit{Feature Data} as in formula \ref{eq:fu-flat}.

### 2017-10-10 Gruba/05-gm.tex
v4.1
v4.1

\begin{definition}
\label{def:gm-it}
An item $E$ involves a blog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of $b$'s owner.
\begin{equation}
\label{eq:gm-it}
E \in
  \begin{cases}
    \text{positive items}       & \quad \text{if } f \text{ \retd{} } b\\
    \text{negative items}  		& \quad \text{if } f \text{ did not \ret{} } b
  \end{cases}
\end{equation}
\end{definition}

And the data of item $E$ could be further divided into three parts.
\begin{itemize}
	\item \textit{User Info}: contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.
	\item \textit{Blog Info}: consists of a metric $C_h$, referring to the correlation between blog contents and recent events returned by Ring \refe{}. $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}). Specifically, each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.
	\item \textit{Interaction Info}: includes three correlation metrics. They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
\end{itemize}
As a result, the obtained group model could learn what does a positive/negative item look like over each metric mentioned above.

>>>>

\begin{definition}
\label{def:gm-it}
An item $E$ involves a blog $b$ and a user $f$ such that $f\ \in R_s(O(b))$, i.e., $f$ is a follower of  the owner of blog $b$.
\begin{equation}
\label{eq:gm-it}
E \in
  \begin{cases}
    \text{positive items}       & \quad \text{if } f \text{ \retd{} } b\\
    \text{negative items}  		& \quad \text{if } f \text{ did not \ret{} } b
  \end{cases}
\end{equation}
\end{definition}

And the data of item $E$ could be further divided into three parts.
%\begin{itemize}

	\stab(1) \stitle{User Info} contains a list of aforementioned metrics \{\#$R_s$, \#$E_s$, $R_{ee}$, \#$B_s$, \#$W_r$\}.

	\stab(2) \stitle{Blog Info} considers the correlation between blog contents and recent events, where the latter is returned by Ring \cite{IEEEexample:ring}. The correlation metric $C_h$ is in the form of a normalized vector with each dimension represents one event (similar as $P_f$ in formula \ref{eq:inte}). Each event could be viewed as a topic $t$, over which the correlation of a blog $b$ could be obtained by formula \ref{eq:simbt}.

	\stab(3) \stitle{Interaction Info} includes three correlation metrics. They are of blog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus $u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent blogs (e.g., within 30 days) in the same manner of $P_f(u)$, and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_t$.
%\end{itemize}
As a result, the obtained group model could learn what does a positive/negative item look like over each metric mentioned above.

### 2017-10-10 Gruba/06-perf.tex
v4.1
v4.1

@@

Experiments were run on a machine with two Intel Xeon E5C2630 2.4GHz CPUs and 64 GB of Memory, running 64 bit Windows 7 professional system.

We have employed a real-world dataset Sina that consists of 24 million blogs that are associated with 43.5K users.

@@

\textbf{Feature Extractor}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
Apparently, \sys{} results the optimal results when $\alpha$ is 0.7, upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million blogs.

@@

\textbf{User Clusterer}
%
Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users and \textit{Data1,...,5} contains 10K randomly selected users each.
Except for \textit{Data1}, solutions with 4 clusters sweep.

@@

\textbf{Behavior Modeler}
%
Fig.\ \ref{fig:10} shows the performance of \sys{} against state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
We compare the metrics of precision, recall, as well as $F_1$ score.
LRC-BQ does not deal with user grouping.
Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), but also examine \sys{} versus LRC-BQ in the case that all users are in mono group (i.e., ``All-Users'').
The results are interesting in that:
\begin{itemize}
	\item With user clustering, \sys{} performs better than LRC-BQ in most cases.
	\item For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
\end{itemize}

>>>>

In this section, we shall first detail the experimental setting of machine info, dataset and parameters; and then present the result and analysis, showing the benefit of \sys{} against state of the art approaches.

@@

Experiments were run on a machine with two Intel Xeon E5C2630 2.4GHz CPUs and 64 GB of Memory, running 64 bit Windows 7 professional system.
%
We have employed a real-world dataset Sina that consists of 24 million blogs that are associated with 43.5K users.

@@

\stitle{Feature Extractor}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
Apparently, \sys{} results the optimal results when $\alpha$ is 0.7, upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million blogs.

@@

\stitle{User Clusterer}
%
Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users and \textit{Data1,...,5} contains 10K randomly selected users each.
Except for \textit{Data1}, solutions with 4 clusters sweep.

@@

\stitle{Behavior Modeler}
%
Fig.\ \ref{fig:10} shows the performance of \sys{} against state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
We compare the metrics of precision, recall, as well as $F_1$ score.
LRC-BQ does not deal with user grouping.
Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), but also examine \sys{} versus LRC-BQ in the case that all users are in mono group (i.e., ``All-Users'').
The results are interesting in that:
%\begin{itemize}

	\stab(1) With user clustering, \sys{} performs better than LRC-BQ in most cases.

	\stab(2) For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ.
%\end{itemize}
